
\chapter{Implementation}
For the implementation of this project we decided to implement a agile methodology approach similar to other projects run at  Haunt. The main process model that we will be taking much of the development process from are aspects of SCRUM. The development was split into multiple sprints, with each containing a requirements gathering stage, development and reflection stage. Each sprint will start with a client meeting with Haunt where we will populate the backlog and develop user stories as requirement gathering. Later on in the development we planned to include meetings with potential users and experts for feedback on the implemented solutions and gather more insight for more efficient user stories. However due to unforeseen circumstances we were only able to gather expert feedback within the final sprint. One of the key features of lean and agile methodology is saving on waste. To try and implement this we will focus on building the core product/prototype first and then gain feedback on the product via user testing to gather more specific features and requirements for the product.

\section{Initial Product}
At the start of the project Haunt had a preliminary proof of concept that needed to be further developed. This initial product contained an API that could add cards, decks and users. The front end consisted a simple view that could display the contents of the decks and cards related to the user. The API was developed in Ruby and followed the RESTful architecture, with the front end developed in JavaScript with Redux js for front end state control. All authorization was done through Auth0 as a temporary solution.

\section{Pre-Development}
Before initial development started we first needed to establish what aspect of the product we would be focusing on. Initially the plan was to develop a potential dashboard for the product. However because development on the main product prototype was no longer in progress via Haunt, this project changed focus to general development of the product.
During the first meetings with the product owner, Rob McGrail, Technical Director at Haunt, we established that some of the underlying technologies on both the front end and api side were either excessive or not long term solutions and needed to be removed. These were identified as state control via redux and the authentication system through Auth0, the first sprint was focused on removing these required technologies to reduce future development time. The later sprints would be focused on refining, adding and fleshing out features in the product.

\input{sprint1}
\input{sprint2}
\input{sprint3}
\input{sprint4}